---
title: "TimeSeriesProjectEDA"
author: "Team - Endgame"
date: "5/31/2019"
output: html_document
---


#Read the prices data and make a subset
```{r}
prices = read.csv('./Data/2sigmaData/2sigma_market_train_data.csv')
head(prices)
```

```{r}
prices[prices['assetName']=='Apple Inc']
```


#cut down the data size

```{r}
str(prices)
```


```{r}
dim(prices)
```


```{r}
prices_recent <- tail(prices,1000000)
dim(prices_recent)
```
```{r}
#
```


```{r}
prices_recent$time <- as.Date(prices_recent$time)
```


```{r}
head(prices_recent,10)
```

```{r}
#Count of records for each day
library(plyr)
#plot(table(prices_recent$time))
counts <- table(prices_recent$time)
daily.count <- count(prices_recent,'time')
dim(daily.count)
barplot(daily.count$freq,col='blue')
plot(counts,col='blue',type='l')

```



# Load news data an subset for last two years
```{r}
news = read.csv('./Data/2sigmaData/news_train_df.csv')
head(news)
```

```{r}
news_recent <- tail(news,3000000)
head(news_recent)
```

#Save Subset dataframes to csv
```{r}
write.csv(prices_recent,'prices_recent.csv')
```

```{r}
write.csv(news_recent,'news_recent.csv')
```



```{r}
dim(prices_recent)
dim(news_recent)
```

```{r}
str(prices_recent)
str(news_recent)
```


```{r}
levels(prices_recent$assetName)
```

```{r}
apple = prices_recent[prices_recent$assetName=="Apple Inc",]
head(apple)
```

```{r}
apple_news = news_recent[news_recent$assetName =='Apple Inc',]
head(apple_news)
```

```{r}
appleClosingPrice = apple$close
appleOpeningPrice = apple$open
plot(appleClosingPrice,type='l',col='red')
lines(appleOpeningPrice,type='l',col='green')
```

```{r}
library(forecast)
(apple.model1 <- auto.arima(appleOpeningPrice,stepwise = F,approximation = F))
```

```{r}
ggAcf(diff(appleOpeningPrice))
```

```{r}
ggAcf(apple.model1$residuals)
```

```{r}
Box.test(apple.model1$residuals,type = 'Ljung-Box',lag=20)
```

```{r}
checkresiduals(apple.model1)
```


```{r}
(apple.model2 <- arfima(appleOpeningPrice))
```

```{r}
checkresiduals(apple.model2)
```

```{r}
dim(apple_news)
```

```{r}
length(apple_news$sentimentClass)
```

```{r}
count(apple_news,'time')
```



```{r}
head(apple)
```


# Analyze Traget variable for Apple returnsOpenNextMktres10
float64) - 10 day, market-residualized return. This is the target variable used in competition scoring. The market data has been filtered such that returnsOpenNextMktres10 is always not null.
```{r}
plot(apple$returnsOpenNextMktres10,type='l')
```

```{r}
acf(diff(apple$returnsOpenNextMktres10))
```

```{r}
mktres_apple.arima.model1 <- auto.arima(apple$returnsOpenNextMktres10,stepwise = F, approximation = F)
```

```{r}
checkresiduals(mktres_apple.arima.model1)
```

```{r}
mktres_apple.arFima.model2 <- arfima(apple$returnsOpenNextMktres10)
```

```{r}
checkresiduals(mktres_apple.arFima.model2)
```


```{r}
apple_news['date'] <- as.Date(apple_news$time)
#head(apple_news['date'])
#aggregate(apple_news['time'],by=apple_news['date'],count)
```

```{r}
apple_news_count <- count(apple_news,'date')
plot(apple_news_count$freq,type='l')
```

```{r}
library(ggplot2)
p<-ggplot(data=apple_news_count, aes(x=date, y=freq)) +
  geom_bar(stat="identity")
p
```

```{r}
apple_new_doi <- apple_news[,c('date','sentimentClass')]
head(apple_new_doi)
```

```{r}
apple.daily.sentiment <- aggregate(apple_new_doi['sentimentClass'],by=apple_new_doi['date'],sum)
plot(apple.daily.sentiment,type='l')
```

```{r}
apple.daily.sentiment['assetCode'] = "AAPL.O"
head(apple.daily.sentiment)
```

```{r}
#head(apple)
apple['date'] = as.Date(apple$time)
head(apple)
```

```{r}
merge(apple, apple.daily.sentiment,by='date')
```

#True Sentiment
```{r}
apple_news['trueSentiment']<- (apple_news$sentimentPositive - apple_news$sentimentNegative) * (apple_news$sentimentWordCount/apple_news$wordCount)
head(apple_news)
```

